\section{Scrum tools}\label{preStudy:scrum}
This pre-study is aimed to finding a useful tool for managing the agile software development work flow carried out throughout the project.

Here follows a list of features that is, more or less, requirements. Further more it should preferably be free to use for Open Source Software.

\subsection*{Must haves}
\begin{itemize}
\item A \gls{scrum:board} to organize tasks in categories, e.g. \textit{Ready}, \textit{In progress} and \textit{Done}.
\item A way to manage a backlog of tasks to do.
\end{itemize}

\subsection*{Nice to haves}
\begin{itemize}
\item Automatic integrated handling of task progress with source control tools, i.e. \textit{GitHub}.
\item A way to visualize the history of how tasks got processed.
\end{itemize}

In a general search of solutions the products \textit{Trello} from Trello, Inc., \textit{ZenHub} from Launch Labs, Inc. and \textit{Waffle} from CA Technologies was spotted and further analyzed.

Here follows a brief description of each product.

\subsection*{Trello}
A simple To Do list web application that enables users to arrange \textit{cards}, i.e. tasks in columns of the users desires and as such fulfills the \textit{must have} requirements.
\textit{Cards} can be assigned labels, check lists, members and has its own discussion board associated.

\subsection*{ZenHub}
A fully featured project management tool to handle agile processes around software development. 
It is integrated with the \textit{GitHub} web application, that is used for source control of the software, by use of a browser extension and enables the users to handle sprints, work flow visualization and integration with \textit{GitHub} task management. 
This product meets the \textit{must have} requirements as well and further more integrates with \textit{GitHub} and enables visualization of the work done.
It does however require the users to install a browser extension on each development environment.

\subsection*{Waffle}
A web application powered by \textit{GitHub} work flow actions. 
It visualizes the current tasks to do, tasks doing and tasks ready for review in a user specified column setup. 
It allows for creating new issues and more from the web application and picks up changes from \textit{GitHub} as well. 
It meets both the \textit{must have} and \textit{nice to have} requirements.

\subsection*{Conclusion}
All products meet the \textit{must have} requirements but only \textit{ZenHub} and \textit{Waffle} integrates with \textit{GitHub} and they are all free to use when working with \gls{oss}.
Between \textit{Waffle} and \textit{ZenHub} a main difference is that the latter one requires installation of browser extensions that currently is supported on the \textit{Chrome} browser from Google, Inc. and \textit{Firefox} browser from Mozilla, Inc.  \citep{preStudy:scrum:zenhub}.
\textit{Waffle} is instead accessible to everyone through the website and because of this \textit{Waffle} is chosen as the \gls{scrum} tool.
