\chapter{Requirements}\label{ch:Requirements}
This chapter defines the requirements for the project. 
The functional requirements are described with \glspl{userstory} with some additional conditions of satisfaction to increase the testable details and add non-functional requirements.

\section*{User stories}

\userstory{As a consultant, I want to use a tablet to access the system}

Device operating systems to support includes: \newline
\begin{tabularx}{\textwidth}{X}
    Apple iOS 8 and 9 \\
    Android 4.2, 4.3, 4.4, 5.0, 5.1 and 6.0
\end{tabularx}

This covers 92.4\% and 91.5\% of \textit{Android} and \textit{iOS} devices respectively, according to the distribution tables in appendices \ref{appendix:androidDistribution} and \ref{appendix:appleDistribution}.

\userstory{As a consultant, I want to input user information when beginning a session and automatically add them to the user database}

If internet is present, the user information must be submitted immediately to the database.

If internet is not present, the user information must be stored on the device for later automatic submission.

Information to input must include the following fields:\newline
\field[The full name of the user]{name}{string}
\field{email}{string}
\field{birthday}{Date}
\field[Years of experience]{experience}{int}
\field[Type of racket from predefined list]{racketType}{RacketType}
\field[Allow comparison to other users]{isComparisonAllowed}{boolean}

\userstory{As a consultant, I want to start a session with a user and record data from the racket}

Information is transmitted from racket to the system with \textit{\gls{bluetooth:ble}}. 

Information saved for a session must include: \newline
\field{consultant}{Consultant}
\field[Date of the recording session]{date}{Date}
\field{location}{Location}
\field[Recorded racket data]{racketDate}{RacketData}
\field{user}{User}

\userstory{As a consultant, I want to show details of recorded data to specific users}

Measured data to be presented as numbers or graphs: \newline
\field[Number of strokes]{strokes}{int}
\field[Most used types of strokes from predefined types]{types}{Array<StrokeType>}
\field[Maximum racket speed in m/s]{maxRacketSpeed}{double}
\field[Maximum shuttlecock speed in m/s]{maxShuttleCockSpeed}{double}

\userstory{As a user, I want to receive an email with a generated password for my account, when a consultant have created an account on my behalf}

When a consultant creates an account on behalf of a user, the user should be able to access that account with an auto generated password send to his account after creation.

If internet is present, the email must be submitted immediately.

If internet is not present, the email must be stored on the device for later automatic submission.

\userstory{As a user, I want to be able to change my password from within the application}

If internet is not present, this operation is not possible.

\userstory{As a user, I want to compare my performance data to other users}

Users that allows comparison must be able to be matched on ranking lists.

Ranking lists must be available on the following metrics: \newline
\begin{tabularx}{\textwidth}{X}
    Number of total strokes \\
    Number of strokes on specific predefined stroke types \\
    Racket speed \\
    Shuttlecock speed \\
\end{tabularx}

\userstory{As a user, I want to share my user profile on social media}

Social media includes \textit{Facebook} and \textit{Twitter}.

The shared information must be a summary of the performance, possibly edited by the user, and a link to the complete user profile on the web page.

\userstory{As a user, I want to see my recorded data compared to historical data}

If a user has multiple recorded sessions, metrics must be presented in comparison with the previously recorded metrics.
