\chapter{Introduction}
This chapter gives a brief introduction to the project and how it is expected to be solved.
The main problem to solve is:

\userstory{Enable athletes to monitor, visualize and track their performances, in an accessible way, when exercising}

The overall platform aims to enable collaboration between athletes, coaches, administration and other stakeholders in the badminton clubs to gain better achievements and progress for the athletes.

With a ''smart'' badminton racket that can record details of how it is used, the athletes performance can be tracked. 
This racket will communicate with a device what parses the recorded data and presents the measurements in an understandable way to the athlete and coach.
The recorded data is saved in the system for later comparison with the athlete or its friends and for the coach to analyse to better understand the individual athletes weaknesses.

MAYBE INSERT VISION HERE?

\section*{Relevance}
Sports wearables are on the rise with new products launching every month. 
Most large technology companies like \textit{Apple, Inc.} and \textit{Samsung} are investing heavily into the market and \textit{Gartner, Inc.} predicts that ''\textit{From 2015 through 2017, smartwatch adoption will have 48 percent growth(...)}'' \citep{introduction:relevance:gartner}.

New products that enables users to understand their performances and activities are in high demand, but most of the wearables are centred around wristbands and smart phone applications. 
These have certain limitations and the precision of the data gathered can be of poor quality.
The product of this project if different. 
It is in the center of the action and gives precise measurements of what forces act on the racket.
With this in mind the product is different in the technological sense but fits the same user demand of existing wearables.

\section*{Work process}
The project process is managed with the agile SCRUM development framework. 
Tasks are managed in a backlog and pulled into sprints of two weeks. 
The process of adding tasks to the backlog are done in groomming sessions where the next parts of the project is discussed and reflection, i.e., retrospective, of tasks not finished or newly arisen issues are weighted and prioritized.

Visualization of tasks and their state is done with an online scrum board. 
The tool to use is decided in a pre-study, see section \ref{preStudy:scrum}.

There is no delegation of specific tasks, e.g., front-end and back-end. 
Instead tasks are solved as time and prioritization sees fit.
